ChemKED: a human- and machine-readable data standard for chemical kinetics experiments

### 2017-07-25 pyked.tex
few final edits

Nonetheless, databases of fundamental combustion experiments
have been shown to be quite useful. For instance, Olm and colleagues used their
ReSpecTh-based database to quantify the performance of literature
hydrogen~\autocite{Olm:2014gn} and syngas~\autocite{Olm:2015ch} kinetic models,
and more recently develop improved models for hydrogen\slash
syngas~\autocite{Varga:2016gj} and ethanol~\autocite{Olm:2016et}. In all four
cases, they converted numerous experimental datasets from the literature into
the ReSpecTh standard.

@@

The \pybox|write_file()| method writes a new \ck{} YAML file based on
the class' instance attributes, while \pybox|convert_to_ReSpecTh()| converts the \pybox|ChemKED|
instance to a ReSpecTh XML file. In the latter case, some information may be lost, as \ck{}
files both encode more details and specify more granularity of some information than
ReSpecTh files.

>>>>

Nonetheless, databases of fundamental combustion experiments
have proved quite useful. For instance, Olm and colleagues used their
ReSpecTh-based database to quantify the performance of literature
hydrogen~\autocite{Olm:2014gn} and syngas~\autocite{Olm:2015ch} kinetic models,
and more recently develop improved models for hydrogen\slash
syngas~\autocite{Varga:2016gj} and ethanol~\autocite{Olm:2016et}. In all four
cases, they converted numerous experimental datasets from the literature into
the ReSpecTh standard.

@@

The \pybox|write_file()| method writes a new \ck{} YAML file based on the instance attributes
of the class, while \pybox|convert_to_ReSpecTh()| converts the \pybox|ChemKED|
instance to a ReSpecTh XML file. In the latter case, some information may be lost, as \ck{}
files both encode more details and specify more granularity of some information than
ReSpecTh files.
